---
  title: "Implementation Examples of multi-level meta-analytic models with robust variance estimators and using Bayesian approaches to deal with non-independent effect sizes"
  author: Shinichi Nakagawa, Alistair M. Senior, Wolfgang Viechtbauer and Daniel W. A. Noble
  date: "`r Sys.Date()`"
  bibliography: refs.bib
  csl: science.csl
  output: 
    bookdown::html_document2:
      code_folding: hide
      number_sections: no
      toc: yes
      toc_depth: 6
      toc_float: yes
    bookdown::word_document2:
      toc: no
      toc_depth: 6
      number_sections: true
      reference_docx: template.docx
  editor_options: 
    chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE, tidy = TRUE, fig.width = 10)
## numbers >= 10^5 will be denoted in scientific notation,      ## numbers >= 10^5 will be denoted in scientific notation,
  ## and rounded to 2 digits      ## and rounded to 2 digits
  options(digits = 2)
```

# Introduction
Here, we demonstrate using some simple simulated data how meta-analyst's can implement some simple methods to correct for inflated Type I error rates when using multilevel models with non-independent effect size data. For ease of presentation, we use simulated data throughout and demonstrate two of the simplest and most effective methods that are most robust to a wide array of contexts that a meta-analyst might be faced with in analyzing their data.

# R Packages Required

First, we'll load some of the packages that we'll need.

```{r packages_data}
  ##################################
  # Clean workspace
  ##################################
      rm(list=ls())

  ##################################
  # Loading packages & Functions
  ##################################
      install.packages("pacman")
      pacman::p_load(tidyverse, kableExtra, gridExtra,  MCMCglmm, brms,  metafor, robumeta)
```

# Simulating non-independent effect size data




# Robust Variance Estimator Correction (Method 6)


# Bayesian Multi-level Meta-analytic Model (Method 9)